\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 body.tex
Working on Example for Linkage Transformer.
move tabulars
clean up linkage tranformer appendix
working on all-typing-rule.tex

\section{Metatheory in (pseudo-)Agda}
We make four agda source code files (publicly and anonymously) openly avaliable, and they include the corresponding QIIT syntax definition and models.

@@

\section{Typing Rules in one Figure}
\include{all-typing-rule.tex}

\section{Metatheory, in detail}

\label{sec:metatheory}
\input{metatheory.tex}

\section{Example in Metatheory}\label{sec:coqexample}
\input{coq-example.tex}

>>>>

\section{Metatheory in (pseudo-)Agda}
\label{sec:agda-files}
We make four agda source code files (publicly and anonymously) openly avaliable, and they include the corresponding QIIT syntax definition and models.

@@

\section{A More Complete Set of Typing Rules for \TT}
\input{all-typing-rule.tex}

\section{Using \TT's Linkage Transformers to Model a Derived Family}
\input{stlc-linkTran-typing.tex}

\if 0
\section{Metatheory, in detail}
\label{sec:metatheory}
\input{metatheory.tex}

\section{Example in Metatheory}\label{sec:coqexample}
\input{coq-example.tex}
\fi

### 2022-11-10 metatheory-condensed.tex
working on all-typing-rule.tex

\noindent
A supplemental appendix gives a more complete example
showing how families are modeled and
type-checked using linkages and linkage transformers.

>>>>

\noindent
A supplemental appendix sketches how the other introduction forms of linkage transformers
can be used to model the construction of a derived family as a linkage transformer.
